### 2009-03-17 doc/ws-programming-tutorial/doc/tex_echoservice/echoservice.tex
Corrections

	\item \textbf{Binding} --- The protocol and the data format used for the message transmission are denoted in the element \textit{binding}. Possible style attributes are \textit{document} or \textit{rpc} (Remote Procedure Call). The transport attribute defines the protocol which is regularly HTTP. For each operation a corresponding SOAP action has to be defined which assignes a messages to be either \textit{literal} or \textit{encoded}~\cite{BUTEK_2009}. The service implemented in this chapter will use the binding \textit{document}/\textit{literal} and the protocol HTTP which is to be seen in the lines followed by  line~\ref{lst_code:echo_wsdl_binding}.

@@

A SOAP fault message is always located within the body element and can appear only one time. 
It indicates error messages in case the port type \textit{solicit-response} (input, output, fault) has been chosen.
An element called \textit{fault} encapsulates diffrent types of elements which are describing the fault.
These elements are listed in Table~\ref{tbl:fault_elements}.
\begin{table}[h]
 \centering
 \caption{Elements of the fault message.}
 \label{tbl:fault_elements}
	\begin{tabular*}{\textwidth}[t]{p{2cm}p{13cm}}
	\hline
	\textbf{Element}        & \textbf{Description}\\
	\hline
	\textbf{faultcode} 	& Code which shall identify the fault.\\
	\textbf{faultstring} 	& A human readable explanation of the fault.\\
	\textbf{faultactor} 	& Information about who caused the fault to happen.\\
	\textbf{detail}         & Holds application specific error information.\\
	\hline\\
	\end{tabular*}
\end{table}
The fault code describes the generic class of the fault. The ARC implementation assigns each fault a certain number.
The fault code along with its description is described within the Table~\ref{tbl:faultcode}
\begin{table}[h]
 \centering
 \caption{Possible fault codes.}
 \label{tbl:faultcode}
	\begin{tabular*}{\textwidth}[t]{p{2cm}p{4cm}p{9cm}}
	\hline
	\textbf{Fault code} & \textbf{Error} & \textbf{Description}\\
	\hline
	0 & \textbf{undefined}       & --- \\
	1 & \textbf{unknown}         & Reason for failure couldn't be identified.\\
	2 & \textbf{VersionMismatch} & Found an invalid namespace for the SOAP Envelope element.\\
	3 & \textbf{MustUnderstand}  & The processing of the SOAP header is optional unless the flag mustUnderstand is set ``true''. If, according to that case, the SOAP service is not able to understand the header a fault message with the faultcode MustUnderstand is returned. \\
	4 & \textbf{Client}          & The request message was incorrectly formed or contained incorrect information.\\
	5 & \textbf{Server}          & There was a problem with the server so the message could not proceed \\
	6 & \textbf{DataEncodingUnknown} & The message couldn't be processed due to encoding problems\\
	\hline
	\end{tabular*}
\end{table}

For morde information about WSDL it is recommended to check the internet address~\href{http://www.w3.org/TR/wsdl}{http://www.w3.org/TR/wsdl}.

@@

This section presents the implementation of the service defined in the WSDL file of the previous section.
The source code is shown in Listing~\ref{lst:echo_service_cpp}.
The header file will be set aside for it contains only redundant information. 
It can be reread in the source directory that is accompanying the tutorial.
Regarding to the source code of the Echo Web Service basically three changes of the Time Web Service source code are required.
The first change concerns the constructor and can be found at line~\ref{lst_code:echo_cpp_prefix}.
Two strings are extracted of the server configuration file which are later used to envelope the message before it is returned.
Furthermore, a new method \textit{makeFault} in line~\ref{lst_code:echo_cpp_makeFault} has been introduced which is able to create a fault messages.
Within the method \textit{process} two new code fragments are now extracting and analyzing the incoming message, to be seen at line~\ref{lst_code:echo_cpp_extracting} and \ref{lst_code:echo_cpp_analyzing}.
In case something unexpected happens both will create a SOAP fault message.\\
% Vielleicht noch etwas über das extrahieren der Nachricht schreiben

@@

Again, the HED is configured by an XML file and launched in the same manner as introduced before.
The server configuration file is shown in Listing~\ref{lst:echo_hed_configuration_xml}.
The only change concerns the lines~\ref{lst_code:echo_hed_configuration_xml_pre} and \ref{lst_code:echo_hed_configuration_xml_pre} which specify the \textit{prefix} and \textit{suffix}.
The parameters will be extracted in the constructor of the service and explain nicely how settings can be passed from the server configuration file towards the service.

@@

With the interface of the server gaining complexity, so is the code for the client - for two reasons. Firstly, because the additional arguments need to be filled. Secondly, because of the extra effort to interact with the (here human) user to collect the data which needs to be forwarded to the Echo Web Service. The source code of the client is shown Listing~\ref{lst:client_echo_cpp}.
The parameters are now passed by the command line, to be seen in the lines followed by line~\ref{lst_code:echo_client_cpp_arguments}.
That code is independent from the ARC library.
The creation of the SOAP client is unchanged and the request is created in the lines subsequent to line~\ref{lst_code:echo_client_cpp_request}.
It is processed in the code after line~\ref{lst_code:echo_client_cpp_response} in which is also the response is received.
The checks of the response have expanded by an additional condition which tests for a fault message, see line~\ref{lst_code:echo_client_cpp_fault}.

>>>>

	\item \textbf{Binding} --- The protocol and the data format used for the message transmission are denoted in the element \textit{binding}. Possible style attributes are \textit{document} or \textit{rpc} (Remote Procedure Call). The transport attribute defines the protocol which is regularly HTTP. For each operation a corresponding SOAP action has to be defined which assignes a messages to be either \textit{literal} or \textit{encoded}~\cite{BUTEK_2009}. The service implemented in this chapter will use the binding \textit{document}/\textit{literal} and the protocol HTTP which is to be seen in the lines follow line~\ref{lst_code:echo_wsdl_binding}.

@@

A SOAP fault message is always located within the body element and can appear only once. 
It indicates error messages in case the port type \textit{solicit-response} (input, output, fault) has been chosen.
An element called \textit{fault} encapsulates different types of elements that describe the fault.
These elements are listed in Table~\ref{tbl:fault_elements}.
\begin{table}[h]
 \centering
 \caption{Elements of the fault message.}
 \label{tbl:fault_elements}
	\begin{tabular*}{\textwidth}[t]{p{2cm}p{13cm}}
	\hline
	\textbf{Element}        & \textbf{Description}\\
	\hline
	\textbf{faultcode} 	& Code which shall identify the fault.\\
	\textbf{faultstring} 	& A human readable explanation of the fault.\\
	\textbf{faultactor} 	& Information about who caused the fault to happen.\\
	\textbf{detail}         & Holds application specific error information.\\
	\hline\\
	\end{tabular*}
\end{table}
The fault code describes the generic class of the fault. The ARC implementation assigns each fault a certain number.
The fault code along with its description is described within the Table~\ref{tbl:faultcode}
\begin{table}[h]
 \centering
 \caption{Possible fault codes.}
 \label{tbl:faultcode}
	\begin{tabular*}{\textwidth}[t]{p{2cm}p{4cm}p{9cm}}
	\hline
	\textbf{Fault code} & \textbf{Error} & \textbf{Description}\\
	\hline
	0 & \textbf{undefined}       & --- \\
	1 & \textbf{unknown}         & Reason for failure couldn't be identified.\\
	2 & \textbf{VersionMismatch} & Found an invalid namespace for the SOAP Envelope element.\\
	3 & \textbf{MustUnderstand}  & The processing of the SOAP header is optional unless the flag mustUnderstand is set ``true''. If, according to that case, the SOAP service is not able to understand the header a fault message with the faultcode MustUnderstand is returned. \\
	4 & \textbf{Client}          & The request message was incorrectly formed or contained incorrect information.\\
	5 & \textbf{Server}          & There was a problem with the server so the message could not proceed \\
	6 & \textbf{DataEncodingUnknown} & The message couldn't be processed due to encoding problems\\
	\hline
	\end{tabular*}
\end{table}

For more information additional tutorials can be found in the appendix or check the internet address~\href{http://www.w3.org/TR/wsdl}{http://www.w3.org/TR/wsdl}.

@@

This section presents the implementation of the service defined in the WSDL file of the previous section.
The source code is shown in Listing~\ref{lst:echo_service_cpp}.
The header file will be set aside since it contains only redundant information. 
It can be reread in the source directory that is accompanying the tutorial.
In comparsion with Time Web Service, basically three changes are required.
The first change concerns the constructor and can be found at line~\ref{lst_code:echo_cpp_prefix}.
Two strings are extracted of the server configuration file which are later used to envelope the message before it is returned.
Furthermore, a new method \textit{makeFault} in line~\ref{lst_code:echo_cpp_makeFault} has been introduced which is able to create a fault messages.
Within the method \textit{process} two new code fragments are now extracting and analyzing the incoming message, to be seen at line~\ref{lst_code:echo_cpp_extracting} and \ref{lst_code:echo_cpp_analyzing}.
In case something unexpected happens either will create a SOAP fault message.\\
% Vielleicht noch etwas über das extrahieren der Nachricht schreiben

@@

Again, the HED is configured by an XML file and launched in the same manner as introduced before.
The server configuration file is shown in Listing~\ref{lst:echo_hed_configuration_xml}.
The only change concerns the lines~\ref{lst_code:echo_hed_configuration_xml_pre} and \ref{lst_code:echo_hed_configuration_xml_suf} which specify the \textit{prefix} and \textit{suffix}.
The parameters will be extracted in the constructor of the service and explain nicely how settings can be passed from the server configuration file towards the service.

@@

With the interface of the server gaining complexity, so is the code for the client - for two reasons. Firstly, because the additional arguments need to be filled. Secondly, because of the extra effort to interact with the (here human) user to collect the data which needs to be forwarded to the Echo Web Service. The source code of the client is shown Listing~\ref{lst:client_echo_cpp}.
The parameters are now passed by the command line, to be seen in the lines following line~\ref{lst_code:echo_client_cpp_arguments}.
That code is independent from the ARC library.
The creation of the SOAP client is unchanged from the Echo client's implementation and the request to the server is created in the lines subsequent to line~\ref{lst_code:echo_client_cpp_request}.
It is processed in the code after line~\ref{lst_code:echo_client_cpp_response} in which also the response is received.
The checks of the response have expanded by an additional condition which tests for a fault message, see line~\ref{lst_code:echo_client_cpp_fault}.

### 2009-03-17 doc/ws-programming-tutorial/doc/tex_introduction/introduction.tex
Corrections

This document gently introduces to the preparation of standalone Web Services and cognate clients with the Advance Resource Connector (ARC).
The reader is guided through a series of practically oriented examples.
Each is accompanied by explanations of the main concepts of the software architecture.
No particular skills are required to follow the presented steps.
It is however beneficial to have some basic comprehension of the programming language C++, the file format XML and any regular UNIX shell.
To start, the user shall have an installation of ARC-1, as it is performed with current RPM or .deb packages\footnote{see http://wiki.nordugrid.org for explicit instructions for setup}.

The ARC server provides access to services.
These are executed on the same machine that the server is installed on.
Some services, like the A-REX service, will delegate computational efforts to other machines
via additional software like a local queueing system.
But the A-REX service itself does not migrate away to other machines - at least this
has not been implemented yet.
Services may comprise computational tasks (e.g., some secret and strongly
patented algorithm), allow arbitrary computations (like ARC's A-REX or
Amazon's clouds) or provide access to other resources like a particular
database or to arbitrary disk space (like ARC's hopi or bartender).

The users of computational services are software tools, too.
They are referred to as clients.
It is those clients that perform the interactions with a human user.
However, when a service requests a performance of another service at the same or another server, then this first service is in the role of a client, too.

Servers provide access to a single service or a set of services. For ARC, there is one service, named Hosting Environment Demon (HED), that is more special than other services: HED organises the assignment of other services on the same server to the network. But this does not break the concept, it is only a commodity. If services are not busy reacting to a client's request, then they are waiting. The task of servers can be subdivided into:
\begin{itemize}
 \item Wait for client request
 \item Receive the request
 \item Perform the desired service
 \item Create a response for the client
 \item Send response to the client
 \item Wait for next client request
\end{itemize}
While the server waits passively for a request, the client acts actively:
\begin{itemize}
 \item Create a request
 \item Transmit the request to the server which provides the desired service.
 \item Wait for the reply
 \item Receive the response from the server.
 \end{itemize}
\forcelinebreak

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=13cm]{tex_introduction/HED2.pdf}
	\mycaption{Example of a HED structure providing a Web Service}{The HED consists of several layers which are connected with each other. The arrow indicate the message flow of the used configuration. The MCCs and Services may hold a SecHandler in order to give additional security. Additional modules (on the left) are used within the HED. \task{Why is the Web Service in all images outside of the HED?}}
\label{fig:HED_internal}
\end{figure}

As to be seen, the MCCs are connected which each other and passing incoming and outgoing message to the upper or the respective lower layer. In case of outgoing messages a MCC is wrapping the data of the upper layer as a payload into their own protocol (while incomming message will be unwrapped).
The lowest layer has to be a transport protocol like TCP which enables the transmission between two applications.
Technically there are even lower layers required needed for the communication but they are already realised within the operating system and the  network card.
TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream.
Above the TCP layer is the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired (i.e. for authentication), the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) has to be inserted between the TCP and HTTP layers.
The HTTP provides the client-server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by ARC to multiplex between different services. The multiplexing layer can also be defined within the HED and is called Plexer.
Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service~\cite{QIANG_2005}.\\
% QUESTION: Why is the plexer always illustrated  being above the SOAP MCC. There's no config file example like that in the tree.
%In my understanding (because plexer is not my initial idea), plexer (as a sort of hub) can be put at both after http or soap. If you put after soap,then you are doing switching for different web services. While I put it after http, because somehow, I need to switch the message after http-processing, in more detail, one branch for soap and then web service/s, one branch for a non-soap service/server (the SP Service is not a service based on SOAP, actually it is based on http, so it is kind of web application).

>>>>

This document gently introduces to the preparation of standalone Web Services and cognated clients with the Advance Resource Connector (ARC).
The reader is guided through a series of practically oriented examples.
Each is accompanied by explanations of the main concepts of the software architecture.
No particular skills are required to follow the presented steps.
It is however beneficial to have some basic comprehension of the programming language C++, the file format XML and any regular UNIX shell.
To start, the user shall have an installation of ARC-1, as it is performed with current RPM or .deb packages\footnote{see http://wiki.nordugrid.org for explicit instructions for setup}.\\

The ARC server provides access to services.
These are executed on the same machine that the server is installed on.
Some services, like the A-REX service, will delegate computational efforts to other machines
via additional software like a local queueing system.
But the A-REX service itself does not migrate away to other machines - at least this
has not been implemented yet.
Services may comprise computational tasks (e.g., some secret and strongly
patented algorithm), allow arbitrary computations (like ARC's A-REX or
Amazon's clouds) or provide access to other resources like a particular
database or to arbitrary disk space (like ARC's hopi or bartender).\\

Services are invoked using software programs, which are referred to as clients. 
These programs may directly perform the interactions of human users or request a performance of other services of another server (here the first service is in the role of a client, too).
The tasks of servers and clients are well defined. If servers are not busy reacting to a client's request, then they are waiting. The task of servers can be subdivided into:
\begin{itemize}
 \item Wait for client request
 \item Receive the request
 \item Perform the desired service
 \item Create a response for the client
 \item Send response to the client
 \item Wait for next client request
\end{itemize}
While the server waits passively for a request, the client acts actively:
\begin{itemize}
 \item Create a request
 \item Transmit the request to the server which provides the desired service.
 \item Wait for the reply
 \item Receive the response from the server.
 \end{itemize}
Servers provide access to a single or a set of services. In ARC services are provided by the Hosting Environment Demon (HED) which enables the installation of several services on one network access point. 
\forcelinebreak

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=13cm]{tex_introduction/HED2.pdf}
	\mycaption{Example of a HED structure providing a Web Service}{The HED consists of several layers which are connected with each other. The arrow indicate the message flow of the used configuration. The MCCs and Services may hold a SecHandler in order to give additional security. Additional modules (on the left) are used within the HED. \task{Why is the Web Service in all images outside of the HED?} } % TODO: Reverse order of layers, s.t. the highest layers are above and the lowest layer are at the bottom
\label{fig:HED_internal}
\end{figure}

The MCCs are connected which each other and passing incoming and outgoing message to the upper or the respective lower layer. In case of outgoing messages a MCC is wrapping the data of the upper layer as a payload into their own protocol (while incomming message will be unwrapped).
The lowest layer has to be a transport protocol like TCP which enables the transmission between two applications.
Technically there are even lower layers required needed for the communication but they are already realised within the operating system and the  network card.
TCP is well suited for the application because it provides a reliable and ordered delivery of a byte stream.
Above the TCP layer is the Hypertext Transfer Protocol (HTTP). 
In case a security layer is desired (i.e. for authentication), the TLS (Transport Layer Security formerly known as SSL, Secure Sockets Layer) has to be inserted between the TCP and HTTP layers.
The HTTP provides the client-server architecture. It is stateless but offers several extensions for requests, header information and status codes. Furthermore HTTP enables the usage of Uniform Resource Locators (URL) which is used by ARC to multiplex between different services. The multiplexing layer can also be defined within the HED and is called Plexer.
Depending on the path of the URL the Plexer passes messages to a defined SOAP service which again passes the message to the Web Service~\cite{QIANG_2005}.\\
% QUESTION: Why is the plexer always illustrated  being above the SOAP MCC. There's no config file example like that in the tree.
%In my understanding (because plexer is not my initial idea), plexer (as a sort of hub) can be put at both after http or soap. If you put after soap,then you are doing switching for different web services. While I put it after http, because somehow, I need to switch the message after http-processing, in more detail, one branch for soap and then web service/s, one branch for a non-soap service/server (the SP Service is not a service based on SOAP, actually it is based on http, so it is kind of web application).
